---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)

my_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vS8jkQNy7udecOnL97KVYAL6c9trKni3LpPiQ7cdnT68-DbNhsejs7O8QYPS1BywAjGZ7Ba3MSMy9fB/pub?output=csv")

updated_data <- my_data %>%
  rename(
    meal_type = 2,
    location = 3,
    price = 4,
    rating = 5,
    time = 6,
    company = 7
  ) %>%
  mutate(
    location = str_to_lower(location),
    location = str_trim(location),
    location = case_when(
      location == "woolworths" ~ "grocery store",
      TRUE ~ location
    ),
    location = str_to_title(location)
  )

mean_price <- mean(updated_data$price, na.rm = TRUE)
mean_rating <- mean(updated_data$rating, na.rm = TRUE)
home_rating <- mean(updated_data$rating[updated_data$location == "Home"], na.rm = TRUE)
outside_rating <- mean(updated_data$rating[updated_data$location != "Home"], na.rm = TRUE)
```

My eating habits

This report tracks the meals I logged and compares how they differ by cost and rating.
The average meal cost was `r round(mean_price, 2)`, and the average meal rating was `r round(mean_rating, 2)` out of 5.


```{r}
updated_data %>%
  ggplot(aes(x = meal_type, y = price)) +
  geom_bar(stat = "summary", fun = "mean", fill = "steelblue") +
  labs(
    title = "Mean meal cost by meal type",
    x = "Meal type",
    y = "Average cost (NZD)"
  ) +
  theme_classic()
```

```{r}
updated_data %>%
  ggplot(aes(x = location, y = rating)) +
  geom_bar(stat = "summary", fun = "mean", fill = "seagreen") +
  labs(
    title = "Average meal rating by location",
    x = "Location",
    y = "Average rating"
  ) +
  theme_classic()
```

The avereage meal rating was `r round(mean_rating, 2)` out of 5, and meals eaten at home had an average rating of `r round(home_rating, 2)`, while meals eaten outside had an average rating of `r round(outside_rating, 2)`.
